Multiway Spherical Clustering via \\ Degree-Corrected Tensor Block Models

### 2023-01-24 tensor_clustering/IEEE/ieee_submission/ieee_v3.tex
organize

\begin{thm}[Error for angle-based iteration]\label{thm:refinement} Consider the setup as in Theorem~\ref{thm:initial}. Assume the local linear stability of degree holds in the neighborhood $\tN(z,\epsilon)$ for $\epsilon = \log^{-1}p$. Suppose 
$r=\tO(1)$ and $\text{SNR} \geq \tilde C p^{-K/2}\log p$ for some large constant $\tilde C$. Let $z^{(t)}$ denote the $t$-th iteration output in Sub-algorithm~\hyperref[alg:main]{2} with initialization $z^{(0)}$ from Sub-algorithm~\hyperref[alg:main]{1}. With probability going to 1, there exists a contraction parameter $\rho \in (0,1)$ such that 
\begin{align}\label{eq:final}
    \ell(z, \hat z^{(t+1)}) \lesssim &\ \KeepStyleUnderBrace{
   \text{SNR}^{-1}
    \exp\of{- \frac{p^{K-1}\text{SNR}}{r^{K-1}}}}_{\substack{\text{statistical error}} }+ \KeepStyleUnderBrace{ \rho^t \ell(z, z^{(0)}). }_{\substack{\text{computational error}}}
\end{align}
\end{thm}
From the conclusion~\eqref{eq:final}, we find that the iteration error is decomposed into two parts: statistical error and computational error. The statistical error is unavoidable with noisy data regardless $t$, whereas the computational error decays in an exponential rate as the number of iterations $t \rightarrow \infty$.

>>>>

\begin{thm}[Error for angle-based iteration]\label{thm:refinement} Consider the setup as in Theorem~\ref{thm:initial}. Assume the local linear stability of degree holds in the neighborhood $\tN(z,\epsilon)$ for $\epsilon \geq \log^{-1}p$. Suppose 
$r=\tO(1)$ and $\text{SNR} \geq \tilde C p^{-K/2}\log p$ for some sufficiently large constant $\tilde C$. Let $z^{(t)}$ denote the $t$-th iteration output in Sub-algorithm~\hyperref[alg:main]{2} with initialization $z^{(0)}$ from Sub-algorithm~\hyperref[alg:main]{1}. With probability going to 1, there exists a contraction parameter $\rho \in (0,1)$ such that 
\begin{align}\label{eq:final}
    \ell(z, \hat z^{(t+1)}) \lesssim &\ \KeepStyleUnderBrace{
   \text{SNR}^{-1}
    \exp\of{- \frac{p^{K-1}\text{SNR}}{r^{K-1}}}}_{\substack{\text{statistical error}} }+ \KeepStyleUnderBrace{ \rho^t \ell(z, z^{(0)}). }_{\substack{\text{computational error}}}
\end{align}
\end{thm}
From the conclusion~\eqref{eq:final}, we find that the iteration error is decomposed into two parts: statistical error and computational error. The statistical error is unavoidable with noisy data regardless $t$, whereas the computational error decays in an exponential rate as the number of iterations $t \rightarrow \infty$.
